---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{pctalks}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Project Description



### Required Features


## Existing Work

PositConf 2024 talks platform used green colors and cards as shown in [this video](https://youtube.com/shorts/rAfBnkZOCxI?feature=share).



## Deliverables

**Start date: 2025-02-05**  
**End date:   2025-02-19**

- Day 1 and 2:
  - [ ] Initial wireframing. You may use AI tools such as [tldraw](https://www.tldraw.com/), [shiny assistant](https://gallery.shinyapps.io/assistant/#) or [ploomber AI editor](https://editor.ploomber.io/)
  - Framework to use:
    - [ ] shiny only
    - [x] [golem](https://github.com/ThinkR-open/golem)
    - [ ] [rhino](https://github.com/Appsilon/rhino)
    - [ ] shiny + [ambiorix](https://ambiorix.dev/)
- Day 3:
  - [ ] First meeting for discussing UI and features
- Day 12:
  - [ ] Second meeting for discussing deployment
- Day 15 or before:
  - [ ] Deployment


## How to Contribute

- Fork this repository
- Create a new branch for your feature
- Make your changes
- Submit a pull request
- Wait for review and address any feedback



## Installation

You can install the development version of `{pctalks}` like so:

```{r}
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
pctalks::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("pctalks")
```

```{r, error = TRUE}
covr::package_coverage()
```
